\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeaward}[2]{
    \item
    \begin{tabular*}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Peng Chen} \\ \vspace{1pt}
    Shanghai, China \\ \vspace{1pt}
    \small 
    \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{pengchzn@gmail.com}} ~ 
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/pengchzn}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western University}{September 2025 -- Expected August 2026}
      {Master of Science in Statistics}{London, Canada}
    \resumeSubheading
      {Shanghai Institute of Technology}{September 2019 -- June 2024}
      {Bachelor of Science in Computer Science, GPA: 4.0 (Rank: 1/129)}{Shanghai, China}
        \begin{itemize}
                \item\small Main Courese: Data Structures(92), Data Mining $\&$ Analysis(83), Development of Information System(91), Compilers Principles(99), etc.
        \end{itemize}
  \resumeSubHeadingListEnd

%------Research Interest-------
\section{RESEARCH INTERESTS}
\ Machine Learning, \ Statistical Learning, \ Optimization, \ AI for Science, \ Natural Language Processing



%-----------Publication-----------
\section{Publication}
\textbf{J-plus: A catalogue of globular cluster candidates around the m81/m82/ngc3077 triplet of galaxies}\\
\textit {Monthly Notices of the Royal Astronomical Society} \hfill {Published} \\
\textbf{A fast QR-based Principal Component Analysis implementation via torch}\\
\textit{Astronomy and Computing} \hfill{Published} \\
\textbf{Yonder: A python package for data denoising and reconstruction}\\
\textit {Research Notes of the AAS} \hfill{Published}\\

%-----------Research-----------
\section{Research / Intern}
  \resumeSubHeadingListStart

    \resumeSubheading
      {JSTI Group Limited}{October 2024 -- May 2025}
      {Algorithm Engineer}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{\textbf{Research Topic:} Developing a Balancing System for Regional Road Networks Under High Passenger Flow Conditions with Overlaying Influencing Factors.}
        \resumeItem{\textbf{Dynamic Management System for Emergency Lane:} Conducted a thorough analysis of various influencing factors affecting high passenger flow on highways to assess optimal conditions for the utilization of hard shoulders.}
        \resumeItem{\textbf{Quantitative Model System for Imbalance Points:} Created multiple predictive models for traffic flow, incorporating variables such as high passenger volume, weather conditions, and accident occurrences to identify and quantify road network imbalance points.}
        \resumeItem{\textbf{Regional Road Network Balancing Strategy:} Designed an integrated balancing strategy, consisting of upstream diversion, midstream flow control, and downstream discharge mechanisms, effectively enhancing the capacity and efficiency of the regional road network.}
      \resumeItemListEnd

    \resumeSubheading
      {labml.ai Deep Learning Paper Implementations}{May 2024 -- Present}
      {Contributor}{Github}
      \resumeItemListStart
        \resumeItem{Spearheaded the optimization and translation of project content, focusing on improving clarity and accessibility for a global audience, particularly Chinese-speaking users.}
        \resumeItem{Conducted meticulous reviews and edits of documentation to enhance comprehension and usability, ensuring accurate and high-quality translations that maintain the integrity of the original content.}
        \resumeItem{Contributed to the project's increasing popularity and engagement, helping it become a go-to resource for deep learning enthusiasts and professionals alike. The project now has \textbf{59.1k} stars and \textbf{6.0k} forks on GitHub.}
      \resumeItemListEnd

    \resumeSubheading
      {Reconstructing the movement of neutrinos with deep learning}{September 2023 -- June 2024}
      {Undergraduate Thesis}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Developed a deep neural network model to reconstruct the movement direction of neutrinos from complex sensor data. Incorporated GPT attention blocks into a Transformer architecture, enhancing the model's ability to process long-sequence data.}
        \resumeItem{Received recognition as an \textbf{outstanding paper} by my institute for the innovative approach and thorough research conducted.}
      \resumeItemListEnd

    \resumeSubheading
      {DataWhale}{May 2023 -- Present}
      {Member}{Online}
      \resumeItemListStart
        \resumeItem{Engaged as a proactive member of DataWhale, a distinguished open-source organization with a focus on advancing the fields of data science and artificial intelligence through community-driven learning and collaboration.}
        \resumeItem{Played a key role in educational initiatives reaching over 10,000 learners, demonstrating a significant impact on data science and AI learning globally.}
        \resumeItem{Actively involved in DataWhale, an open-source community focused on data science and AI, contributing as a Teaching Assistant for major projects like \textbf{AIGC Specialized Study} and \textbf{Dive into Deep Learning} alongside Professor Li Mu.}
      \resumeItemListEnd

    \resumeSubheading
      {Hello-Algo}{October 2022 -- Present}
      {Contributor}{Github}
      \resumeItemListStart
        \resumeItem{Actively contributed to the development and enhancement of Hello-Algo, an acclaimed open-source tutorial designed to introduce learners to Data Structures and Algorithms.}
        \resumeItem{Designed and implemented user-friendly Python examples and exercises, aimed at demystifying complex data structures and algorithms for beginners through practical, hands-on learning experiences.}
        \resumeItem{Supported the project's growth and recognition in the developer and educational communities, with the project now boasting \textbf{110.0k} stars and \textbf{13.7k} forks on GitHub, indicating its widespread acceptance and use.}
      \resumeItemListEnd

          \resumeSubheading
      {Shanghai Astronomical Observatory, Chinese Academy of Sciences}{July 2021 -- June 2022}
      {Visiting Scholar}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Working on topic: \textbf{Discovering new galactic and extragalactic stellar association with statistical learning.}}
        \resumeItem{Applied advanced statistical learning to analyze astronomical data, identifying new stellar associations using spectra and time series data, enhancing our understanding of galaxy structures.}
        \resumeItem{Created \textbf{QRPCA}, a PyTorch-enhanced algorithm, improving PCA efficiency and accuracy, speeding up astronomical data analysis.}
        \resumeItem{Developed \textbf{Yonder}, a specialized tool designed for effective data denoising and dimensionality reduction, aiding in astronomical research data preprocessing.}
      \resumeItemListEnd

    \resumeSubheading
      {Science American}{January 2021 -- May 2022}
      {Translation Intern}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Led the translation of cutting-edge scientific articles in areas including Computer Science and Artificial Intelligence, facilitating the dissemination of complex concepts to a broader audience.}
        \resumeItem{Conducted extensive research to grasp and accurately translate specialized terminology and concepts, enhancing the accessibility of advanced scientific knowledge.}
        \resumeItem{Adapted complex scientific ideas into engaging and accessible language, contributing to the global understanding of interdisciplinary scientific advancements.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------Awards-----------
\section{Awards and Scholarships} 
{China Robot Competition FIRA Simulation Group 5 Vs 5}{, \bf National 2nd Prize} \hfill{\em November, 2020}\\
{China Robot Competition FIRA Simulation Group 11 Vs 11}{,\bf  National 3nd Prize} \hfill{\em November, 2020}\\
{DongHua Cup College Student Cyber Security Invitational}{ \bf,National 3nd Prize} \hfill{\em December, 2022}\\
{The Seventh Shanghai College Student Cyber Security Competition}{ ,\bf Shanghai 2nd Prize} \hfill{\em December, 2022}\\
{Scholarship of Shanghai Insititute of Technology}{, \bf 2nd Prize} \hfill{\em November, 2023}\\

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programing Languages}{: Python, C++, R} \\
     \textbf{Technologies/Frameworks}{: Linux, Pytorch, Numpy, Pandas} \\
     \textbf{Languages}{: Mandarin(native), English(CET-6 550, Duolingo 120)} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Artifical Intellgence Club}{Autumn 2020 -- Present}{President}{Shanghai Institute of Technology}
            \resumeItemListStart
                \resumeItem{Led the Artificial Intelligence Club, focusing on teaching Python and machine learning, enhancing the AI understanding of members across various skill levels.}
                \resumeItem{Honed leadership, organizational, and communication skills, successfully managing club operations and external collaborations.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}

